On Extending a Full-Sharing Multithreaded Tabling Design with Batched Scheduling

### 2015-05-26 paper.tex
paper -> revising 1

In this section, we describe our proposal to support the combination
of batched scheduling with the FS design. Remember that batched
scheduling requires further support to work with the FS design
because, with batched scheduling, we have to detect when a newly found
answer is also a new answer for the thread at hand in order to ensure
that new answers for a given subgoal call are correctly propagated one
and only once to all thread’s repeated calls. To solve that, we propose
an extension to the table space data structures, which we named
\emph{Private Answer Chaining} (PAC), as a way to keep track, per
thread and subgoal call, of the answers that were already found and
propagated to the thread's repeated calls.

\begin{figure}[!ht]
%\vspace{-\intextsep}
\centering
\includegraphics[width=10.5cm]{figures/pcc_key-idea.pdf}
\caption{PAC splits answer propagation and answer representation}
\label{fig_tabtries_pcc_key-idea}
%\vspace{-1.0\intextsep}
\end{figure}

>>>>

In this section, we describe our proposal to support the combination
of batched scheduling with the FS design. Remember that batched
scheduling requires further support to work with the FS design
because, with batched scheduling, we have to detect when a newly found
answer is also a new answer for the thread at hand in order to ensure
that new answers for a given subgoal call are correctly propagated one
and only once to all thread’s repeated calls. In the FS design answer
representation and answer propagation is stored in the answer trie
data structure, thus threads are unable to know if they have or not
have propagated an answer whenever it appears during the
evaluation. To solve that, we propose an extension to the table space
data structures, which we named \emph{Private Answer Chaining} (PAC),
as a way to keep track, per thread and subgoal call, of the answers
that were already found and propagated to the thread's repeated
calls. Figure~\ref{fig_tabtries_pcc_key-idea} illustrates the key idea
of the PAC strategy. In a nutshell, PAC splits answer representation
from answer propagation, and allows the first to be kept publicly
shared among threads in the answer trie data structure, and the second
to be privately stored in the subgoal frame data structure of each
thread. Thus, with PAC, whenever a answer appears during the
evaluation, a thread knows if the answer was already propagated or not
propagated, just by consulting its own subgoal frame data structure.

\begin{figure}[!ht]
%\vspace{-\intextsep}
\centering
\includegraphics[width=10.5cm]{figures/pcc_key-idea.pdf}
\caption{PAC splits answer representation and answer propagation}
\label{fig_tabtries_pcc_key-idea}
%\vspace{-1.0\intextsep}
\end{figure}
